---
title: "analysis"
author: "Ronit Dash"
format: html
execute:
  echo: false
---

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
library(stringr)
```
<!-- Wisdom: -->

<!-- Question: Which crimes are most likely to result in a culprit being found? -->

<!-- Specific Question: If someone was to be the victim of a crime in Britain, how likely would a culprit be found? -->

<!-- Units: Each Crime in Britain -->
<!-- Outcome: Whether the culprit was found or not. -->
<!-- Covariates: Crime Type, Location -->

Being a victim of a crime is a common fear for tourists when visiting places like England. To determine how often suspects are found for each type of crime, I used data from the UK police database for the month of May. I modeled SuspectIdentified, a TRUE/FALSE variable that listed whether a suspect was found and/or punished for a crime, as a logistic function of crime type. This lead me to the conclusion that the crimes that (the average tourist could possibly be a victim of) have the highest rate of catching a culprit are Burglary and theft with 3.06% and 2.87% on average respectively. These values could be as high as 7.71% or low as .9% for Burglary and high as 22.1% or low as .1% for Theft.

```{r}
#| label: data
x <- read.csv("West_Midlands_Crime.csv")
set.seed(123)
crime <- x |> sample_frac(.10) |> 
  mutate(type = as.factor(Crime.type), outcome = Last.outcome.category, area = LSOA.name)|> filter(outcome != "")
crime <- crime |> mutate(SuspectIdentified = ifelse(outcome %in% c(
    "Offender given a caution",
    "Awaiting court outcome", 
    "Action to be taken by another organisation", 
    "Awaiting court outcome",
"Formal action is not in the public interest",
"Further action is not in the public interest"), 1, 0)) |> 
  select(SuspectIdentified, type, area)
```

```{r}
ndata <- tibble(type = c( "Bicycle theft",
 "Burglary", 
 "Criminal damage and arson", 
                      "Drugs",
                 "Other crime", "Other theft", 
                      "Possession of weapons",  
                 "Public order",  
                     "Robbery",
                 "Shoplifting",  
       "Theft from the person",
               "Vehicle crime", "Violence and sexual offences"))
```

```{r}
#| cache: true
#| label: model
#| warning: false
fit <- brm(formula = SuspectIdentified ~ type,
           data = crime,
           family = bernoulli(),
           iter = 1200,
           warmup = 600,
           chains = 2,
           refresh = 0,
           silent = 2,
           seed = 99)
```

```{r}
model_data <- fit |> add_epred_draws(newdata = ndata)
# model_data |> filter(.epred >= .001) |> 
#   summarize(lowst_value = min(.epred, na.rm = TRUE))
# max_epred_per_type <- model_data %>%
#   group_by(type) %>%
#   summarize(max_epred = max(.epred)) # This code was used to determine high and low confidence intervals.

model_data |>   filter(.epred >= 0.001) |>
ggplot(aes(y = type, x = .epred)) +
  stat_slab(aes(fill = type), position = "dodge", show.legend = FALSE) +
  scale_x_log10() +
  labs(
    title = "Average Percentage Chances of Culprits being found",
    subtitle = "The amount of crimes that find a culprit seem to be low",
    y = "Type",
    x = "Probability of Suspect Identification", fill = NULL
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 45, hjust = 1))
```

